\vskip-0.6in \Large Political Uncertainty

### 2016-01-27 GS-extension.tex
add conjecture for what drives case of 1 NNB

		Solving for the determinant of this matrix:
		\[
		  (-1)\cdot 
			\left|\begin{array}{cccc}
				0 & 0 & 0 & -1\\
				- 1 & 0 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}  \\
			0 & 0 & \frac{\partial^2 L}{\partial b(0)^2} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)} \\
			0 & -1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
			\end{array} \right|
		=
						  (-1)\cdot (-1) \cdot (-1)
			\left|\begin{array}{ccc}
				- 1 & 0 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}  \\
			0 & 0 & \frac{\partial^2 L}{\partial b(0)^2}\\
			0 & -1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}
			\end{array} \right| =
		\]
		\[
		  (-1) \cdot (-1)
			\left|\begin{array}{cc}	
			0 & \frac{\partial^2 L}{\partial b(0)^2}\\
			-1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}
			\end{array} \right| = 0 - (-1) \cdot \frac{\partial^2 L}{\partial b(0)^2} = \frac{\partial^2 L}{\partial b(0)^2}
		\]
		\item Thus we need $\frac{\partial^2 L}{\partial b(0)^2} < 0$
			\begin{itemize}
				\item This boils down to $\left(e^{-X} - 1\right) < 0$
				\item Implies $X > 0$
				\item i.e. $-\al + b(0) > 0$ or $b(0) > \al$
			\end{itemize}
		\item It is NOT the case that $b(0)$ has to be such that $X=Y$ even though $b\left(\frac{1}{2}\right) =0$. In fact, it seems in numerical examples that this does \textit{not} happen.
			\begin{itemize}
				\item However, I do see that this existence of the one non-negative bribe (NNB) is not common. It exists for $\al = 0$ and WB = 8, but goes away as soon as $\al = 0.1$ or $W_B$ = 9.
				\item In both cases, I can see that changing the parameter would push the value of $b(0)$ over $0.5$, making $X > Y$. This is when the solution switches to 2 NNB's.
			\end{itemize}
		\item Can write out SOC (just after equation 33) and FOC, sub together to get
			\[
			  \frac{1}{1 + e^{-X}} \left(e^{-Z} - 1\right) < 0
			\]
			Not sure what this means
	\end{itemize}

>>>>

		Solving for the determinant of this matrix:
		\[
		  (-1)\cdot 
			\left|\begin{array}{cccc}
				0 & 0 & 0 & -1\\
				- 1 & 0 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}  \\
			0 & 0 & \frac{\partial^2 L}{\partial b(0)^2} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)} \\
			0 & -1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}
			\end{array} \right|
		=
						  (-1)\cdot (-1) \cdot (-1)
			\left|\begin{array}{ccc}
				- 1 & 0 & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}  \\
			0 & 0 & \frac{\partial^2 L}{\partial b(0)^2}\\
			0 & -1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}
			\end{array} \right| =
		\]
		\[
		  (-1) \cdot (-1)
			\left|\begin{array}{cc}	
			0 & \frac{\partial^2 L}{\partial b(0)^2}\\
			-1 & \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}
			\end{array} \right| = 0 - (-1) \cdot \frac{\partial^2 L}{\partial b(0)^2} = \frac{\partial^2 L}{\partial b(0)^2}
		\]
		\item Thus we need $\frac{\partial^2 L}{\partial b(0)^2} < 0$
			\begin{itemize}
				\item This boils down to $\left(e^{-X} - 1\right) < 0$
				\item Implies $X > 0$
				\item i.e. $-\al + b(0) > 0$ or $b(0) > \al$
			\end{itemize}
		\item It is NOT the case that $b(0)$ has to be such that $X=Y$ even though $b\left(\frac{1}{2}\right) =0$. In fact, it seems in numerical examples that this does \textit{not} happen.
			\begin{itemize}
				\item However, I do see that this existence of the one non-negative bribe (NNB) is not common. It exists for $\al = 0$ and WB = 8, but goes away as soon as $\al = 0.1$ or $W_B$ = 9.
				\item In both cases, I can see that changing the parameter would push the value of $b(0)$ over $0.5$, making $X > Y$. This is when the solution switches to 2 NNB's.
				\item {\color{blue} CONJECTURE}: Group B chooses 1 NNB until it would be large enough to make $X > Y$ (when $\al \approx 0$) or $Z > Y$ (when $\al$ large and negative), then switch to 2 NBB
					\begin{itemize}
						\item {\color{blue} This is not strictly true around $-0.7$}
						\item When $\al$ is large and positive, go straight from 0 NNB to 2 NNB
					\end{itemize}
			\end{itemize}
		\item Can write out SOC (just after equation 33) and FOC, sub together to get
			\[
			  \frac{1}{1 + e^{-X}} \left(e^{-Z} - 1\right) < 0
			\]
			Not sure what this means
	\end{itemize}
